Understanding Expectation Formation from Probabilistic Surveys

### 2019-07-02 slides/ExpSlidesAfterDraft.tex
Created a new version of slides for Draft results. Working on it.

%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

@@

$$y_{t+1} = \rho y_t + \omega_t  $$ 
$$\omega_t \sim N(0,\sigma^2_{\omega})$$

\begin{itemize}
	\item $0 < \rho \leq 1$
	\item if $\rho =0$, no way to forecast at all
	\item $\omega_t$ is i.i.d 
\end{itemize}

@@

\subsection{Sticky Expectation}

@@

$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
$$\textrm{SE} \quad \quad  \lambda = 0.4 $$ 
\begin{figure}
	\includegraphics[scale=0.25]{figures/ir_indse} 
\end{figure}
\end{frame}

@@

\begin{figure}
	\includegraphics[scale=0.25]{figures/ir_popse} 
\end{figure}

@@

\subsection{Other theories}

@@

\begin{figure}
	\includegraphics[height=6.3cm,width=10cm]{figures/ir_indseni} 
\end{figure}

@@

\begin{figure}
	\includegraphics[height=6.3cm,width=10cm]{figures/ir_popseni} 
\end{figure}

@@

\begin{figure}
	\includegraphics[height=8cm,width=8cm]{figures/ni_illustration} 
\end{figure}

@@

\begin{figure}
	\includegraphics[height=5cm,width=8cm]{figures/rigidity} 
\end{figure}

@@

\begin{frame}{Population moments: average}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_med.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: average forecast errors}
\begin{figure}
	\includegraphics[scale=0.3]{figures/fe_fe.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: average uncertainty}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_var.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: average uncertainty}
\begin{figure}
	\includegraphics[scale=0.3]{figures/var_var.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_disg.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_disg.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/disg_disg.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: uncertainty and disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/var_disg.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: uncertainty and disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/var_disg2.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: forecast and realization}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_true.png} 
\end{figure}
\end{frame}

@@

\begin{frame}{Test of Rational Expectation}
\begin{table}[tbhp] \centering \adjustbox{max height=\dimexpr\textheight-5.5cm\relax, max width=\textwidth}{
	\begin{tabular}{lllllll}
		\hline 
		& SPFCPI\_FElvl       & SPFPCE\_FElvl & SPFCPI\_Vardiff & SPFPCE\_Vardiff & SPFCPI\_Disgdiff & SPFPCE\_Disgdiff            \\
		\hline 
		L.InfExp\_FE        & 0.941***      & 1.195***        &                 &                  &                  &           \\
		& (0.0840)      & (0.142)         &                 &                  &                  &           \\
		L2.InfExp\_FE       & -0.313**      & -0.625**        &                 &                  &                  &           \\
		& (0.116)       & (0.198)         &                 &                  &                  &           \\
		L3.InfExp\_FE       & 0.114         & 0.0782          &                 &                  &                  &           \\
		& (0.114)       & (0.196)         &                 &                  &                  &           \\
		L4.InfExp\_FE       & -0.137        & -0.0162         &                 &                  &                  &           \\
		& (0.0820)      & (0.131)         &                 &                  &                  &           \\
		L.InfExp\_Var\_ch   &               &                 & -0.855***       & -0.565**         &                  &           \\
		&               &                 & (0.189)         & (0.162)          &                  &           \\
		L2.InfExp\_Var\_ch  &               &                 & -0.780**        & -0.452*          &                  &           \\
		&               &                 & (0.220)         & (0.186)          &                  &           \\
		L3.InfExp\_Var\_ch  &               &                 & -0.556*         & -0.429*          &                  &           \\
		&               &                 & (0.219)         & (0.189)          &                  &           \\
		L4.InfExp\_Var\_ch  &               &                 & -0.167          & 0.00385          &                  &           \\
		&               &                 & (0.188)         & (0.172)          &                  &           \\
		L.InfExp\_Disg\_ch  &               &                 &                 &                  & -0.571***        & -0.640*** \\
		&               &                 &                 &                  & (0.0699)         & (0.127)   \\
		L2.InfExp\_Disg\_ch &               &                 &                 &                  & -0.376***        & -0.0944   \\
		&               &                 &                 &                  & (0.0764)         & (0.141)   \\
		L3.InfExp\_Disg\_ch &               &                 &                 &                  & -0.0455          & 0.180     \\
		&               &                 &                 &                  & (0.0661)         & (0.138)   \\
		L4.InfExp\_Disg\_ch &               &                 &                 &                  & -0.110*          & -0.0364   \\
		&               &                 &                 &                  & (0.0479)         & (0.123)   \\
		\hline 
		N                   & 143           & 41              & 44              & 44               & 146              & 44        \\
		R-sq                & 0.593         & 0.750           & 0.384           & 0.322            & 0.356            & 0.496    \\
		\hline 
	\end{tabular}
}
\end{table}
\end{frame}

@@

\begin{figure}
	\includegraphics[scale=0.3]{figures/inf_shocksQ.png} 
\end{figure}

@@

\begin{figure}
	\includegraphics[scale=0.3]{figures/RigidityJPEFigure2.png} 
\end{figure}

@@

\begin{frame}{Inflation IR to  shocks exluding monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/CPIAU_ashocks_nmp.png} 
\end{figure}

@@

\begin{frame}{Inflation IR to  shocks including monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/CPIAU_ashocks.png} 
\end{figure}

@@

\begin{frame}{Inflation IR to  shocks excluding monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/PCEPI_ashocks_nmp.png} 
\end{figure}

@@

\begin{frame}{Inflation IR to  shocks including monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/PCEPI_ashocks.png} 
\end{figure}

\subsection{Benchmark Results from Professional Forecasters }

\begin{frame}{Forecasting errors IR to  shocks excluding monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFFE_ashocks_nmp.png} 
\end{figure}

\begin{frame}{Forecasting errors IR to monetary policy shocks}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFFE_ashocks.png} 
\end{figure}

\begin{frame}{Disagreements IR to shocks excluding monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFDisg_ab_ashocks_nmp.png} 
\end{figure}

\begin{frame}{Disagreements IR to  monetary policy shocks}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFDisg_ab_ashocks.png} 
\end{figure}

\begin{frame}{Uncertainty IR to shocks excluding monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFVar_ab_ashocks_nmp.png} 
\end{figure}

\begin{frame}{Uncertainty IR to monetary policy shocks}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFVar_ab_ashocks.png} 
\end{figure}

>>>>

\usepackage{threeparttable}
\usepackage{caption}
\usepackage{subcaption}

%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

@@

$$y_{t} = \rho y_{t-1} + \omega_t  $$ 
$$\omega_t \sim N(0,\sigma^2_{\omega})$$

\begin{itemize}
	\item $0 < \rho \leq 1$
	\item if $\rho =0$, no way to forecast at all
	\item $\omega_t$ is i.i.d. (allowing for $\sigma^2$ to be time-varying) 
\end{itemize}

@@

\subsection{Sticky Expectation(SE)}

@@

$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
$$\textrm{SE} \quad \quad  \lambda = 0.4 $$ 
\begin{figure}
	\includegraphics[scale=0.25]{figuresDraft/ir_indse} 
\end{figure}
\end{frame}

@@

\begin{figure}
	\includegraphics[scale=0.25]{figuresDraft/ir_popse} 
\end{figure}

@@

\subsection{Noisy Information(NI)}

@@

\begin{figure}
	\includegraphics[height=6.3cm,width=10cm]{figuresDraft/ir_indseni} 
\end{figure}

@@

\begin{figure}
	\includegraphics[height=6.3cm,width=10cm]{figuresDraft/ir_popseni} 
\end{figure}

@@

\begin{figure}
	\includegraphics[height=8cm,width=8cm]{figuresDraft/ni_illustration} 
\end{figure}

@@

\begin{figure}
	\includegraphics[height=5cm,width=8cm]{figuresDraft/rigidity} 
\end{figure}

@@

\begin{frame}{Uncertainty and Realized Inflation}
\begin{figure}
	\centering
\label{InfVar}
\includegraphics[width=0.33\textwidth]{figuresDraft/Inf1yf_CPIAU_varSCEM.png}
\includegraphics[width=0.33\textwidth]{figuresDraft/Inf1yf_CPIAU_varSPFCPIQ.png}
\includegraphics[width=0.33\textwidth]{figuresDraft/Inf1yf_PCE_varSPFPCEQ.png}
\end{figure}
\end{frame}

\begin{frame}{Uncertainty and Forecast Errors}
\begin{figure}
	\centering
	\label{FEVar}
	\includegraphics[width=0.33\textwidth]{figuresDraft/SPFCPI_FE_varSPFCPIQ.png}
\includegraphics[width=0.33\textwidth]{figuresDraft/SPFPCE_FE_varSPFPCEQ.png}
\includegraphics[width=0.33\textwidth]{figuresDraft/SCE_FE_varSCEM.png}
\end{figure}
\end{frame}

\begin{frame}{Uncertainty and Disagreements}
\begin{figure}
	\centering
\label{DisgVar}
\includegraphics[width=0.33\textwidth]{figuresDraft/CPI_disg_varSPFCPIQ.png}
\includegraphics[width=0.33\textwidth]{figuresDraft/PCE_disg_varSPFPCEQ.png}
\includegraphics[width=0.33\textwidth]{figuresDraft/Q9_disg_varSCEM.png}
\end{figure}
\end{frame}

\begin{frame}{Dispersion of Mean Forecast}
\begin{figure}
	\includegraphics[width=0.33\textwidth]{figuresDraft/IQRmeanCPIQ.png} 
\smallskip
\includegraphics[width=0.33\textwidth]{figuresDraft/IQRmeanPCEQ.png}
\smallskip
\includegraphics[width=0.33\textwidth]{figuresDraft/IQRmeanSCEM.png}
\end{figure}
\end{frame}

\begin{frame}{Dispersion of Uncertainty}
\begin{figure}
	\label{IQR_Unceratitny}
	\includegraphics[width=0.33\textwidth]{figuresDraft/IQRvarCPIQ.png}
\smallskip
\includegraphics[width=0.33\textwidth]{figuresDraft/IQRvarPCEQ.png}
\smallskip
\includegraphics[width=0.33\textwidth]{figuresDraft/IQRvarSCEM.png}
\end{figure}
\end{frame}

\begin{frame}{Distribution of Uncertainty}
\begin{figure}
		\label{Unceratitny_Histogram}
	\includegraphics[width=0.33\textwidth]{figuresDraft/PRCCPIVar1_hist.png}  
\smallskip
\includegraphics[width=0.33\textwidth]{figuresDraft/PRCPCEVar1_hist.png}  
\smallskip
\includegraphics[width=0.33\textwidth]{figuresDraft/SCEvar_hist.png}  
\end{figure}
\end{frame}

\begin{frame}{Distribution of Revision in Forecast}
\begin{figure}
	\includegraphics[width=0.5\textwidth]{figuresDraft/PRCCPIMean01_rv_true_hist.png} 
\includegraphics[width=0.5\textwidth]{figuresDraft/PRCPCEMean01_rv_true_hist.png} 
\end{figure}
\end{frame}

\begin{frame}{Distribution of Revision in Uncertainty}
\begin{figure}
	\includegraphics[width=0.5\textwidth]{figuresDraft/PRCCPIVar01_rv_true_hist.png}  
\includegraphics[width=0.5\textwidth]{figuresDraft/PRCPCEVar01_rv_true_hist.png} 
\end{figure}
\end{frame}

@@

\begin{frame}{Tests of rationality using forecast errors}
	\begin{adjustbox}{totalheight=0.9\textheight}
	\label{NullTestTable}
	\centering 
	\begin{tabular}{llll}
		\hline 
		& SPF CPI          & SPF PCE          & SCE            \\
		\hline 
		\multicolumn{4}{l}{Test 1: Unbiasedness}                                                           \\
		\hline 
		Constant                            & 0.122***         & 0.586***         & 2.220***       \\
		& (0.017)          & (0.061)          & (0.019)        \\
		\hline 
		N                                   & 4697             & 1208             & 67380          \\
		\hline 
		\multicolumn{4}{l}{Test 2: FE does not depend on past information}                                  \\
		\hline 
		Forecast 1-yr before                & 0.307***         & 0.586***         & NA             \\
		& (0.020)          & (0.061)          & NA             \\
		Constant                            & -0.655***        & -0.777***        & NA             \\
		& (0.060)          & (0.116)          & NA             \\
		\hline 
		N                                   & 3429             & 1208             & NA             \\
		$R^2$                 & 0.0721           & 0.118            & NA             \\
		\hline 
		\multicolumn{4}{l}{Test 3: FEs of non-overlapping forecast horizons not serially correlated} \\
		\hline 
		Forecast Error 1-year before        & 0.0756***        & 0.0503***        & NA             \\
		& (0.020)          & (0.035)          & NA             \\
		Constant                            & 0.145***         & 0.275***         & NA             \\
		& (0.021)          & (0.035)          & NA             \\
		\hline 
		N                                   & 3356             & 1208             & NA             \\
		$R^2$                   & 0.00591          & 0.00264          & NA             \\
		\hline 
		\multicolumn{4}{l}{Test 4: Overlapping FEs are only weakly serially correlated}                          \\
		\hline 
		Forecast Error 1-q before           & 0.657***         & 0.834***         & 0.297***       \\
		& (0.025)          & (0.037)          & (0.021)        \\
		Forecast Error 2-q before           & 0.0282           & -0.0858          & 0.308***       \\
		& (0.027)          & (0.048)          & (0.046)        \\
		Forecast Error 3-q before           & -0.0244          & -0.0555          & 0.311***       \\
		& (0.025)          & (0.038)          & (0.045)        \\
		Constant                            & 0.0626***        & 0.113***         & 0.742***       \\
		& (0.019)          & (0.026)          & (0.097)        \\
		\hline 
		N                                   & 2536             & 1004             & 2836           \\
		$R^2$                & 0.439            & 0.552            & 0.232    \\
		\hline      
	\end{tabular}
\end{adjustbox}

\begin{frame}{Test of revision efficiency Using mean revisions}

	\begin{adjustbox}{width=0.9\textwidth}
	\begin{threeparttable}
		\label{RevEfficiency}
		\begin{tabular}{lllllllll}
			\hline 
			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
			\hline 
			\multicolumn{9}{l}{Test 1.  Revision efficiency of mean forecast}            \\
			\hline 
			& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
			\hline 
			L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  \\
			&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   \\
			L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  \\
			&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   \\
			L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     \\
			&               &           &          & (0.048)  &               &           &           & (0.069)   \\
			SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           \\
			&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           \\
			SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** \\
			&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   \\
			& -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   \\
			Constant & (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   \\
			\hline 
			N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       \\
			$R^2$                  & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     \\
			\hline 
		\end{tabular} 
		\begin{tablenotes}
			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
		\end{tablenotes}
	\end{threeparttable}
\end{adjustbox}

\begin{frame}{Test of revision efficiency using uncertainty revisions}

\begin{adjustbox}{width=0.9\textwidth}
	\begin{threeparttable}
		\label{RevEfficiency}
		\begin{tabular}{lllllllll}
			\hline 
			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
			\hline 
			\multicolumn{9}{l}{Test 2. Revision efficiency of uncertainty}                                                            \\
			\hline 
			& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
			\hline 
			L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    \\
			&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   \\
			L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    \\
			&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   \\
			L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    \\
			&               &           &          & (0.121)  &               &           &           & (0.149)   \\
			Constant              & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   \\
			& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   \\
			\hline 
			N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       \\
			$R^2$                 & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723    \\
			\hline 
		\end{tabular} 
		\begin{tablenotes}
			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
		\end{tablenotes}
	\end{threeparttable}
\end{adjustbox}

\begin{frame}{Weak tests of efficiency using changes in forecasts }

	\begin{adjustbox}{width=\textwidth}
	\begin{threeparttable}
		\caption{Weak Tests of Revision Efficiency using Change in Forecasts and Uncertainty}
		\label{WeakRevEfficiency}
		\begin{tabular}{llllllllllllll}
			\hline 
			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
			\hline 
			\multicolumn{14}{l}{Test 3. Weak revision efficiency of change in forecast}                                                                                                                                    \\
			\hline 
			& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
			\hline 
			L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Mean\_ch  &         & -0.433*** & -0.586*** & -0.642*** \\
			&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                    &         & (0.01)     & (0.013)    & (0.025)    \\

			L2.InfExp\_Mean\_ch  &             &           & -0.179*** & -0.242*** &               &           & -0.162*   & -0.200**  & L2.InfExp\_Mean\_ch &         &           & -0.336*** & -0.439*** \\

			&             &           & (0.047)   & (0.049)   &               &           & (0.061)   & (0.067)   &                                   &         &           & (0.018)    & (0.031)    \\
			L3.InfExp\_Mean\_ch  &             &           &           & -0.097**  &               &           &           & -0.088*   & L3.InfExp\_Mean\_ch &         &           & -0.143*** & -0.270*** \\

			&             &           &           & (0.032)   &               &           &           & (0.036)   &                                &         &           & (0.012)    & (0.027)    \\

			&             &           &           &           &               &           &           &           & L4.InfExp\_Mean\_ch &         &           &           & -0.183*** \\

			&             &           &           &           &               &           &           &           &                                 &         &           &           & (0.027)    \\
			&             &           &           &           &               &           &           &           & L5.InfExp\_Mean\_ch &         &           &           & -0.096*** \\
			&             &           &           &           &               &           &           &           &                      &         &           &           & (0.021)    \\
			&             &           &           &           &               &           &           &           & L6.InfExp\_Mean\_ch &         &           &           & -0.044**  \\
			&             &           &           &           &               &           &           &           &                                     &         &           &           & (0.013)    \\
			Constant               & -0.005      & -0.004    & -0.011    & -0.015    & 0.001         & 0.008     & -0.002    & -0.007    & Constant              & -0.055* & -0.034    & -0.001    & -0.002    \\
			& (0.023)     & (0.024)   & (0.026)   & (0.026)   & (0.020)       & (0.020)   & (0.022)   & (0.022)   &                                 & -0.023  & -0.023    & -0.028    & -0.033    \\
			\hline 
			N                    & 1636        & 1430      & 1266      & 1141      & 1402          & 1190      & 1022      & 898       & N                   & 53016   & 43166     & 28850     & 14445     \\
			$R^2$                  & 0.000       & 0.086     & 0.112     & 0.128     & 0.000         & 0.090     & 0.112     & 0.120     & $R^2$ &  0.000       & 0.202     & 0.273     & 0.306   \\
			\hline 
		\end{tabular}
		\begin{tablenotes}
			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
		\end{tablenotes}
	\end{threeparttable}
\end{adjustbox}
\end{frame}

\begin{frame}{Weak Tests of Efficiency using changes in uncertainty}
\begin{adjustbox}{width=\textwidth}
	\begin{threeparttable}
				\label{WeakRevEfficiency}
		\begin{tabular}{llllllllllllll}
			\hline 
			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
			\hline 
			\multicolumn{14}{l}{Test 4. Weak revision efficiency of change in uncertainty}                \\
			\hline                                                                                                                 
			& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean change   & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean change   & t-1       & t-1- t-2  & t-1-t-3   \\
			\hline 
			L.InfExp\_Var\_ch    &             & -0.393**  & -0.568*** & -0.543**  &               & -0.444*** & -0.602*** & -0.658*** & L.InfExp\_Var\_ch    &               & -0.382*** & -0.565*** & -0.652*** \\
			&             & (0.136)   & (0.146)   & (0.177)   &               & (0.094)   & (0.127)   & (0.145)   &                      &               & -0.015    & -0.022    & -0.037    \\
			L2.InfExp\_Var\_ch   &             &           & -0.322**  & -0.278*   &               &           & -0.289*   & -0.404**  & L2.InfExp\_Var\_ch   &               &           & -0.300*** & -0.406*** \\
			&             &           & (0.104)   & (0.132)   &               &           & (0.110)   & (0.137)   &                      &               &           & -0.021    & -0.031    \\
			L3.InfExp\_Var\_ch   &             &           &           & 0.048     &               &           &           & -0.292    & L3.InfExp\_Var\_ch   &               &           & -0.123*** & -0.265*** \\
			&             &           &           & (0.096)   &               &           &           & (0.154)   &                      &               &           & -0.012    & -0.027    \\
			&             &           &           &           &               &           &           &           & L4.InfExp\_Var\_ch   &               &           &           & -0.130*** \\
			&             &           &           &           &               &           &           &           &                      &               &           &           & -0.025    \\
			&             &           &           &           &               &           &           &           & L5.InfExp\_Var\_ch   &               &           &           & -0.058**  \\
			&             &           &           &           &               &           &           &           &                      &               &           &           & -0.018    \\
			&             &           &           &           &               &           &           &           & L6.InfExp\_Var\_ch   &               &           &           & -0.025    \\
			&             &           &           &           &               &           &           &           &                      &               &           &           & -0.012    \\
			Constant               & -0.002      & -0.001    & 0.004     & 0.004     & 0.000         & 0.002     & 0.004     & 0.005     &   Constant                   & -1.339***     & -1.324*** & -1.139*** & -0.839*** \\
			& (0.005)     & (0.005)   & (0.004)   & (0.004)   & (0.004)       & (0.004)   & (0.004)   & (0.004)   &                      & -0.123        & -0.11     & -0.104    & -0.163    \\
			\hline 
			N                    & 1202        & 950       & 765       & 625       & 1078          & 842       & 657       & 519       &                      & 53016         & 43166     & 28850     & 14445     \\
			$R^2$ & 0.000       & 0.120     & 0.265     & 0.242     & 0.000         & 0.233     & 0.321     & 0.385     &                      & 0             & 0.182     & 0.278     & 0.321  \\
			\hline    
		\end{tabular}
		\begin{tablenotes}
			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
		\end{tablenotes}
	\end{threeparttable}
\end{adjustbox}

\subsection{Shock-Based Rigidity}

@@

\begin{figure}
	\includegraphics[width=0.8\textwidth]{figuresDraft/inf_shocksQ.png} 
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.9\textwidth]{figuresDraft/RigidityJPEFigure2.png} 
\end{figure}

@@

\begin{frame}{Technology and oil shocks: 1984-2007}

\begin{figure}
	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/CPIAU_ashocks_nmp_before2007.png}  \\ 
\smallskip
\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFFE_ashocks_nmp_before2007.png} \\
\smallskip
\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFDisg_ab_ashocks_nmp_before2007.png} 
\end{figure}

@@

\begin{frame}{Monetary policy shocks: 1984-2007}

\begin{figure}
	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/CPIAU_ashocks_before2007.png}  \\
	\smallskip 
	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFFE_ashocks_before2007.png} \\
	\smallskip
	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFDisg_ab_ashocks_before2007.png} 
\end{figure}

@@

\begin{frame}{Technology and oil shocks: 1984-2019}

\begin{figure}
	\includegraphics[width=7cm]{figuresDraft/Inf_ashocks.png} 
	\smallskip
	\includegraphics[width=7cm]{figuresDraft/SPFFE_ashocks.png} \\
	\smallskip
	\includegraphics[width=7cm]{figuresDraft/SPFDisg_ab_ashocks.png} 
	\smallskip
	\includegraphics[width=7cm]{figuresDraft/SPFVar_ab_ashocks.png}  
\end{figure}

@@

\begin{frame}{Monetary policy shocks: 1984-2019}

\begin{figure}
	\includegraphics[width=7cm]{figuresDraft/Inf_ashocks_nmp.png}

	\includegraphics[width=7cm]{figuresDraft/SPFFE_ashocks_nmp.png}  \\
	\smallskip 
	\includegraphics[width=7cm]{figuresDratf/SPFDisg_ab_ashocks_nmp.png} 
	\smallskip 
	\includegraphics[width=7cm]{figuresDraft/SPFVar_ab_ashocks_nmp.png}  
\end{figure}
